\bf Forecasts Reconciliation: A geometric view with new insights on bias correction.

### 2019-07-30 Hierarchical-forecast-reconciliation/Figs/orth_pointforerec_schematic.tex
Added some schematics of orthogonal and oblique projections

% Created by tikzDevice version 0.12 on 2019-04-26 17:19:46
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (289.08,505.89);
\begin{scope}
\path[clip] ( 49.20, 61.20) rectangle (263.88,456.69);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 68.84,130.32) --
	( 68.84,317.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 22.07,177.10) --
	(209.16,177.10);

\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] ( 68.84,177.10) -- (232.54,258.95);

\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] (222.59,243.87) --
	(232.54,258.95) --
	(214.51,260.03);

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (238.54,256.65) {{\large $\mathfrak{s}$}};
\definecolor{drawColor}{RGB}{0,0,255}
\definecolor{fillColor}{RGB}{0,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (139.00,317.41) circle (  3.00);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (139.00,335.41) {{\large $\color{blue}{\hat{\bm{y}}}$}};
\definecolor{drawColor}{RGB}{255,0,0}
\definecolor{fillColor}{RGB}{255,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (181.09,233.22) circle (  3.00);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (181.09,209.48) {{\large $\color{red}{\tilde{\bm{y}}}$}};
\definecolor{drawColor}{RGB}{0,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (139.00,317.41) -- (181.09,233.22);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (166.02,243.18) --
	(181.09,233.22) --
	(182.18,251.26);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (139.00,317.41) -- (108.93,197.14);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (103.96,214.51) --
	(108.93,197.14) --
	(121.49,210.13);
\definecolor{fillColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (108.93,197.14) circle (  3.00);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (108.93,173.40) {{\large $\color{black}{{\bm{y}}}$}};
\end{scope}
\end{tikzpicture}

>>>>

% Created by tikzDevice version 0.12 on 2019-07-25 17:17:29
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (289.08,289.08);
\begin{scope}
\path[clip] ( 49.20, 61.20) rectangle (263.88,239.88);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 87.60, 49.44) --
	( 87.60,196.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.84, 86.20) --
	(197.90, 86.20);

\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] ( 87.60, 86.20) -- (216.28,150.54);

\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] (206.33,135.46) --
	(216.28,150.54) --
	(198.25,151.62);

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (222.28,148.24) {{\large $\mathfrak{s}$}};
\definecolor{drawColor}{RGB}{0,0,255}
\definecolor{fillColor}{RGB}{0,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (142.75,196.50) circle (  3.00);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (142.75,214.50) {{\large $\color{blue}{\hat{\bm{y}}}$}};
\definecolor{drawColor}{RGB}{255,0,0}
\definecolor{fillColor}{RGB}{255,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (175.84,130.32) circle (  3.00);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (175.84,106.58) {{\large $\color{red}{\tilde{\bm{y}}}$}};
\definecolor{drawColor}{RGB}{0,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (142.75,196.50) -- (175.84,130.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (160.76,140.27) --
	(175.84,130.32) --
	(176.92,148.35);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (142.75,196.50) -- (119.12,101.96);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (114.15,119.33) --
	(119.12,101.96) --
	(131.68,114.95);
\definecolor{fillColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (119.12,101.96) circle (  3.00);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (119.12, 78.22) {{\large $\color{black}{{\bm{y}}}$}};
\end{scope}
\end{tikzpicture}

### 2019-07-30 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
Added some schematics of orthogonal and oblique projections

\usepackage{amssymb, qtree, bm, multirow, textcmds, siunitx,paralist}
\usepackage{mathrsfs, float, booktabs,todonotes,amsthm, xcolor,sidenotes}
\usepackage[bb=boondox]{mathalfa}
\usepackage{tikz}
\usetikzlibrary{arrows,positioning,shapes,fit,calc}
\usepackage{amsfonts}

@@

@@

	We note that the above result holds when the projection $\bm{SG}$ has the coherent subspace $\mathfrak{s}$ as its image and not for all projection matrices in general. To describe this more explicitly suppose $\bm{SG}$ has as its image  $\mathfrak{L}$ which is itself a a lower dimensional linear subspace of $\mathfrak{s}$, i.e. $\mathfrak{L}\subset\mathfrak{s}$. Then for $\left\{\bm{\mu}_{t+h|t}:\bm{\mu}_{t+h|t}\in\mathfrak{s},\bm{\mu}_{t+h|t}\notin\mathfrak{L}\right\}$,  $\bm{S}\bm{G}\bm{\mu}_{t+h|t} \ne \bm{\mu}_{t+h|t}$. This is depicted in Figure~\ref{fig:Schematic_3D} where $\bm{\mu}_{t+h|t}$ is projected to a point $\bar{\bm{\mu}}$ in $\mathfrak{L}$.  In this case, the reconciled forecast will have as its expectation $\bar{\bm{\mu}}$ rather than $\bm{\mu}_{t+h|t}$ and be biased.

@@

	Our approach to bias correction is to simply estimate the bias by taking the sample mean of $\bm{y_{t+h}}-\hat{\bm{y}_{t+h|t}}$ for all $t+h$ in the training sample.  This can be then subtracted from future forecasts.  As stated in the discussion of MinT, in-sample errors are already used to estimate the optimal direction of projection.  As such we see no problems with using the same errors to bias correct.  Geometrically, the intuition is simple.  In Figure~\ref{fig:MinT_justification1}, the orange points are centered around the origin as would be expected from an unbiased forecast.  If forecasts are biased, then errors should simply be translated until they are centered at the origin.

>>>>

\usepackage{amssymb, qtree, bm, multirow, textcmds, siunitx,paralist}
\usepackage{mathrsfs, float, booktabs,todonotes,amsthm, xcolor,sidenotes, caption, subcaption}

\usepackage[bb=boondox]{mathalfa}
\usepackage{tikz}
\usetikzlibrary{arrows,positioning,shapes,fit,calc}
\usepackage{amsfonts}

@@

	\begin{figure}[H]
		\centering
		%\vspace{-0.9cm}
		\small
		\resizebox{\linewidth}{!}{
			\includegraphics{Figs/OrthProj.pdf}}
		\caption{\textcolor{red}{include caption}}\label{fig:Orthogonal_projection}
	\end{figure}

	\begin{figure}[H]
	\centering
	%\vspace{-0.9cm}
	\small
	\resizebox{\linewidth}{!}{
		\includegraphics{Figs/ObliqueProjection.pdf}}
	\caption{\textcolor{red}{include caption}}\label{fig:Oblique_projection}
	\end{figure}

%		\begin{figure}[H]
%		\centering
%		%\vspace{-0.9cm}
%		\small
%		\resizebox{\linewidth}{!}{
%			\input{Figs/ObliqueProjection}
%		}
%		\caption{\textcolor{red}{write caption}}\label{fig:Oblique_projection}
%	\end{figure}

%\begin{figure}
%	\centering
%	\begin{subfigure}{0.47\textwidth}
%		\resizebox{\linewidth}{!}{
%			\input{Figs/Orth.proj.tex}}
%		\caption{bla bla}
%	\end{subfigure}
%	\begin{subfigure}{0.47\textwidth}
%		\resizebox{\linewidth}{!}{
%			\input{Figs/ObliqueProjection.tex}}
%			\caption{bla bla}
%	\end{subfigure}
%\end{figure}

@@

	We note that the above result holds when the projection $\bm{SG}$ has the coherent subspace $\mathfrak{s}$ as its image and not for all projection matrices in general. To describe this more explicitly suppose $\bm{SG}$ has as its image  $\mathfrak{L}$ which is itself a lower dimensional linear subspace of $\mathfrak{s}$, i.e. $\mathfrak{L}\subset\mathfrak{s}$. Then for $\left\{\bm{\mu}_{t+h|t}:\bm{\mu}_{t+h|t}\in\mathfrak{s},\bm{\mu}_{t+h|t}\notin\mathfrak{L}\right\}$,  $\bm{S}\bm{G}\bm{\mu}_{t+h|t} \ne \bm{\mu}_{t+h|t}$. This is depicted in Figure~\ref{fig:Schematic_3D} where $\bm{\mu}_{t+h|t}$ is projected to a point $\bar{\bm{\mu}}$ in $\mathfrak{L}$.  In this case, the expectation of reconciled forecast will be $\bar{\bm{\mu}}$ rather than $\bm{\mu}_{t+h|t}$ and hence biased.

@@

	Our approach to bias correction is to simply estimate the bias by taking the sample mean of $\bm{y
	}_{t+h}-\hat{\bm{y}}_{t+h|t}$ for all $t+h$ in the training sample.  This can be then subtracted from future forecasts.  As stated in the discussion of MinT, in-sample errors are already used to estimate the optimal direction of projection.  As such we see no problems with using the same errors to bias correct.  Geometrically, the intuition is simple.  In Figure~\ref{fig:MinT_justification1}, the orange points are centered around the origin as would be expected from an unbiased forecast.  If forecasts are biased, then errors should simply be translated until they are centered at the origin.
